% Mohammad Heriyanto
% mheriyanto37@gmail.com
% mheriyanto.wordpress.com
 
\documentclass[12pt,oneside,a4paper]{article}
\usepackage[top=0.5in, bottom=1.25in, left=1.25in, right=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}

\begin{document}

\title{Machine Learning, Deep Learning, and Computer Vision References}
\author{Mohammad Heriyanto \\ email: \href{mailto:mheriyanto37@gmail.com}{mheriyanto37@gmail.com} \\ GitHub: \href{https://github.com/mheriyanto/Data-Science-and-Machine-Learning-References}{https://github.com/mheriyanto}}
   
\maketitle

\begin{abstract}
Repository for Data Science and Machine Learning references.
\end{abstract}

\section{Awesome Lists}
Awesome listrs provide .

\subsection{Artificial Intelligence}
\begin{itemize}
\item Awesome Artificial Intelligence - Lightman Wang
\item Awesome Artificial Intelligence (AI) - Owain Lewis
\end{itemize}

\section{Concepts}
\subsection{Machine Learning Concepts}
\begin{itemize}
\item Pengenalan Pembelajaran Mesin dan Deep Learning (J.W.G. Putra, 2019)
\item Machine Learning Probabilistic Prespective (K.P. Murphy, 2012. The MIT Press)
\end{itemize}

\section{All with Python}
\subsection{Basic Python Books}
\begin{itemize}
\item Python 3 Object-oriented Programming (D. Phillips. 2015. O'Reilly Media)
\item Learning Python Design Patterns (G. Zlobin. 2013. Packt)
\end{itemize}

\section{Courses}
\begin{itemize}
\item  Neural Networks and Deep Learning - Deeplearning.ai by Andrew Ng in YouTube (2010-2014): YouTube
\item Machine Learning - Stanford by Andrew Ng in Coursera (2010-2014): Coursera
\end{itemize}

\section{Deep Learning Frameworks}
\begin{itemize}
\item Deep Learning with PyTorch 1.0 (S. Yogesh K, 2019. Packt): Book and CodeLearning Python Design Patterns (G. Zlobin. 2013. Packt)
\end{itemize}

\section{Research Groups}
\subsection{Universities}
Standford Univ - Machine Learning Group (Prof. Andrew Ng) | Standford Univ - Vision and Learning Lab (Prof. Fei-Fei Li) | Univ of Montreal - Mila (Prof. Yoshua Bengio) | New York Univ - CILVR Lab (Prof. Yann LeCun) | Univ of Toronto - Machine Learning (Prof. Geoffrey Hinton) | Barkeley Univ - Artificial Intelligence Research (BAIR) Lab (Prof. Trevor Darrell)

\section{Datasets}
\begin{itemize}
\item MNIST Dataset - New York University by Yann LeCun (1998): Raw
\item CIFAR10 Dataset - University of Toronto by Alex Krizhevsky (2009): Raw
\end{itemize}

\section{Journals, Magazines, and People}
\subsection{Journals}
\begin{itemize}
\item AI: Artificial Intelligence (Q1) | Journal of Artificial Intelligence Research (Q1) | Artificial Intelligence Review (Q1)
\item Data Science: EPJ Data Science (Q1) | Data Science Journal (Q3)
\end{itemize}

\end{document}